\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CURRICULUM VITAE STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape CURRICULUM VITAE} \\
    \vspace{5pt}
    \textbf{\Large Dr Olasunkanmi S. Arowolo} \\ \vspace{1pt}
    \small Rochester, Kent, United Kingdom $|$ +44 (0)7487 397751 $|$ \href{mailto:oa@olaarowolo.com}{{oa@olaarowolo.com}} \\
    \vspace{3pt}
    \small \faLinkedin\ \href{https://www.linkedin.com/in/olaarowolo/}{linkedin.com/in/olaarowolo} $|$ 
    \faOrcid\ \href{https://orcid.org/0000-0002-5296-6478}{0000-0002-5296-6478} $|$ 
    \faGoogleScholar\ \href{https://scholar.google.com/citations?user=3N_RQWoAAAAJ&hl=en}{Google Scholar} \\
    \vspace{2pt}
    \small \faResearchgate\ \href{https://www.researchgate.net/profile/Sunday-Arowolo}{ResearchGate} $|$ 
    \faTwitter\ \href{https://twitter.com/olaarowolo}{@olaarowolo}
\end{center}

% Set left alignment for all content after header
\raggedright

%-----------EDUCATION & QUALIFICATIONS-----------
\section{Education \& Qualifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PhD in Journalism}{2025}
      {University of Kent}{United Kingdom}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis Title:} Poverty, Politics, and the Press: Uncovering the Complexities of Media Coverage on Nigeria's Social Investment Programmes}
        \resumeItem{Research employs quantitative, qualitative methods including in-depth interviews and thematic analysis using NVivo, SPSS, and CDA}
        \resumeItem{\textbf{Supervisor(s):} Dr. Ben Cocking, Dr. Richard Pendry | \textbf{External Examiner:} Prof. Martin Scott}
      \resumeItemListEnd
    
    \resumeSubheading
      {Master of Science (M.Sc.), Communication Studies [4.01 CGPA]}{2019}
      {Lagos State University}{Nigeria}
    
    \resumeSubheading
      {Bachelor of Science (B.Sc.) (Hons), Mass Communication [4.1 CGPA]}{2014}
      {Lagos State University}{Nigeria}
  \resumeSubHeadingListEnd

%-----------CAREER HISTORY-----------
\section{Career History}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lecturer (Media/Core Communication)}{November 2023 -- December 2024}
      {Health and Social Care, East Kent College, Ashford}{UK}
      \resumeItemListStart
        \resumeItem{Delivered engaging instruction in Health and Social Care to 76 students, with focus on media communication}
        \resumeItem{Developed eight tailored lesson plans incorporating real-world media scenarios}
        \resumeItem{Assessed progress for 76 students, providing constructive feedback}
        \resumeItem{Collaborated with three colleagues to align media aspects with industry standards}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer}{September 2022 -- 2023}
      {Centre for Journalism, University of Kent, Rochester}{UK}
      \resumeItemListStart
        \resumeItem{Delivered teaching for 15-credit 'Studying Journalism' module (JOUR4050) to 23 undergraduate students per semester}
        \resumeItem{Developed and delivered original teaching materials for 13 seminar groups}
        \resumeItem{Set and marked assignments for approximately 23 students}
        \resumeItem{Mentored four undergraduate students as personal tutor}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer (HPL)}{September 2021 -- 2022}
      {School of Social Policy, Sociology \& Social Research, University of Kent}{UK}
      \resumeItemListStart
        \resumeItem{Led seminar teaching for modules SOCI3370 and SOCI5750 for approximately 142 students}
        \resumeItem{Developed instructional materials and learning aids for seminar groups}
        \resumeItem{Evaluated student progress and provided feedback to approximately 56 students}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer}{June 2018 -- May 2021}
      {Department of Journalism, School of Communication, Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{Developed and delivered teaching materials for 950 undergraduate courses}
        \resumeItem{Supervised practical journalism work for 312 students}
        \resumeItem{Conducted student assessments and contributed to research activities}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SELECTED OUTPUTS-----------
\section{Selected Outputs}
\subsection{Peer-Reviewed Journals (Top 5)}
    \resumeItemListStart
        \resumeItem{\textbf{Arowolo, O.}, Yusuf, K., Yahya, J., Lambo, O. and Oduolowu, D. (2023). World Bank Concept of Good Governance, Contemporary Nigerian Democracy, and the Place of the Media. \textit{East African Journal of Interdisciplinary Studies}, 6(1), pp. 54-69. \href{https://doi.org/10.37284/eajis.6.1.1058}{https://doi.org/10.37284/eajis.6.1.1058}}
        \resumeItemListStart
        \resumeItem{Impact: This article examines media's role in governance, influencing policy discussions on democratic accountability in Africa. Cited in policy briefs on media freedom.}
        \resumeItemListEnd
        \resumeItem{Shodipe, O.A., \textbf{Arowolo, O.}, Oloyede, I.B., Alade, M., Fadeyi, I.O. and Oko-Epelle, L. (2024), Visual portrayal of Monkeypox outbreak on BBC: is Western media biased against Africa?, \textit{Global Knowledge, Memory and Communication}. \href{https://doi.org/10.1108/GKMC-09-2023-0317}{https://doi.org/10.1108/GKMC-09-2023-0317}}
        \resumeItemListStart
        \resumeItem{Impact: Highlights media bias in health reporting, informing global health communication strategies and reducing misinformation in pandemics.}
        \resumeItemListEnd
        \resumeItem{Oso Lai, Adeniran, R., \& \textbf{Arowolo, O.} (2024). Journalism Ethics: The Dilemma, Social and Contextual Constraints. \textit{Cogent Social Sciences}. \href{https://doi.org/10.1080/23311886.2024.2328388}{https://doi.org/10.1080/23311886.2024.2328388}}
        \resumeItemListStart
        \resumeItem{Impact: Addresses ethical challenges in journalism, shaping training programs and ethical guidelines for media practitioners in developing contexts.}
        \resumeItemListEnd
        \resumeItem{Suleiman, H., Adedeji, K., \& \textbf{Arowolo, S. O.} (2020). Online Newspaper Coverage of the 8th National Assembly in Nigeria. Media and Communication Review (MCR), Vol. 2, Issue 2, pp. 57–83}
        \resumeItemListStart
        \resumeItem{Impact: Analyzes digital media's role in political accountability, contributing to studies on online journalism and democratic oversight.}
        \resumeItemListEnd
        \resumeItem{\textbf{Arowolo, S.O.} (2015). Uses and Gratification Theory and Tobacco Advertising Necessity: An Exposé. International Journal of Broadcasting and Information Technology, 3(1)}
        \resumeItemListStart
        \resumeItem{Impact: Critiques advertising impacts on public health, influencing regulatory discussions on media content and consumer protection.}
        \resumeItemListEnd
    \resumeItemListEnd

%-----------DETAILS OF RESEARCH FUNDING-----------
\section{Details of Research Funding}
    \resumeItemListStart
        \resumeItem{\textbf{TETFund Doctoral Scholarship} (£115,485.00) -- Awarded 2021, University of Kent, UK. Role: Recipient. Supported PhD research on media coverage of social investment programmes.}
        \resumeItem{\textbf{Research Funding Bid (In Progress):} \textbf{Arowolo, S.O.} (Principal Investigator). Media, Poverty, and Democracy: A Comparative Analysis of Social Investment Discourse in the UK and Nigeria. -- to be submitted August 30, 2025. Estimated value: £50,000. Role: PI.}
        \resumeItem{\textbf{Research Funding Bid (In Progress):} \textbf{Arowolo, S.O.} (Principal Investigator). Democracy by Design? Comparative Governance of Algorithmic Journalism in the UK and Nigeria. -- to be submitted September 15, 2025. Estimated value: £40,000. Role: PI.}
    \resumeItemListEnd

%-----------TEACHING AND SUPERVISION EXPERIENCE-----------
\section{Teaching and Supervision Experience}
    \resumeItemListStart
        \resumeItem{Lecturer, East Kent College (2023-2024): Taught media communication to 76 students, developed lesson plans, assessed progress.}
        \resumeItem{Assistant Lecturer, University of Kent (2022-2023): Delivered 'Studying Journalism' module to 23 students, mentored undergraduates.}
        \resumeItem{Assistant Lecturer, University of Kent (2021-2022): Led seminars for 142 students in social policy modules.}
        \resumeItem{Assistant Lecturer, Lagos State University (2018-2021): Taught 950 undergraduate courses, supervised 312 students in practical journalism.}
        \resumeItem{Graduate Assistant, Lagos State University (2017-2018): Supported teaching for 250 students.}
        \resumeItem{No PGR supervision yet, but mentored 4 undergraduates as personal tutor.}
    \resumeItemListEnd

%-----------PRIZES, AWARDS AND RECOGNITIONS-----------
\section{Prizes, Awards and Recognitions}
    \resumeItemListStart
        \resumeItem{\textbf{British Academy Global Talent Endorsement} (2025) -- Recognised as exceptional talent in academia and research.}
        \resumeItem{\textbf{PhD in Journalism}, University of Kent (2025, no corrections).}
        \resumeItem{\textbf{Runner-Up}, University of Kent Three Minute Thesis (3MT, 2024).}
        \resumeItem{\textbf{ISC² Certified in Cybersecurity} (2024).}
        \resumeItem{\textbf{Qualys Certified Specialist} (2024).}
    \resumeItemListEnd

%-----------COLLABORATIONS AND EXTERNAL ENGAGEMENT-----------
\section{Collaborations and External Engagement}
    \resumeItemListStart
        \resumeItem{Collaborator on British Academy-GRCF funded project (2022-2023): PNEUMA-CITY, University of Kent -- Contributed to research on urban infrastructures.}
        \resumeItem{Founder and CEO, Afriscribe (\href{https://afriscribe.org}{afriscribe.org}) -- Platform for African research dissemination.}
        \resumeItem{Director and Founder, ResearchAfrica (\href{https://researchafrica.pub}{researchafrica.pub}) -- Research network for African scholars.}
        \resumeItem{Blind Peer Reviewer, Global Knowledge, Memory and Communication (Q2 Journal) and Taylor \& Francis.}
        \resumeItem{Member, International Communication Association (ICA), Public Communication of Science and Technology (PCST), Association of Communication Scholars and Professionals of Nigeria (ACSPN), African Council for Communication Education (ACCE), Royal African Society (RAS).}
        \resumeItem{Public engagement: Articles in Vanguard, The Sun, Premium Times on poverty alleviation and media coverage.}
    \resumeItemListEnd

%-----------LEADERSHIP, TRAINING \& MENTORING-----------
\section{Leadership, Training \& Mentoring}
    \resumeItemListStart
        \resumeItem{\textbf{Leadership:} Founder/CEO Afriscribe; Director/Founder ResearchAfrica -- Demonstrated entrepreneurial skills in research dissemination.}
        \resumeItem{\textbf{EDI Contributions:} Committed to inclusive academia; mentored underrepresented students; research on marginalized voices.}
        \resumeItem{\textbf{Training:} Academic trainings in NVivo, SPSS, lectures, feedback, grant writing (UEA, Kent).}
        \resumeItem{\textbf{Mentoring:} Personal tutor for 4 undergraduates; mentored students in journalism practices.}
    \resumeItemListEnd

\end{document}
