\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  DETAILED CURRICULUM VITAE STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape CURRICULUM VITAE} \\
    \vspace{5pt}
    \textbf{\Large Dr Olasunkanmi S. Arowolo} \\ \vspace{1pt}
  \small Lagos, Nigeria $|$ +234 08062081819 $|$ \href{mailto:oa@olaarowolo.com}{{oa@olaarowolo.com}} \\
    \vspace{3pt}
    \small \faLinkedin\ \href{https://www.linkedin.com/in/olaarowolo/}{linkedin.com/in/olaarowolo} $|$ 
    \faOrcid\ \href{https://orcid.org/0000-0002-5296-6478}{0000-0002-5296-6478} $|$ 
    \faGraduationCap\ \href{https://scholar.google.com/citations?user=3N_RQWoAAAAJ&hl=en}{Google Scholar} \\
    \vspace{2pt}
    \small \faResearchgate\ \href{https://www.researchgate.net/profile/Sunday-Arowolo}{ResearchGate} $|$ 
    \faTwitter\ \href{https://twitter.com/olaarowolo}{@olaarowolo}
\end{center}

% Set left alignment for all content after header
\raggedright

%-------------------------------------------

%-----------SUMMARY-----------
\section{Summary}
\small{Highly motivated and skilled researcher with a PhD in Journalism, endorsed by the British Academy as Global Talent in Media and Communication (2025), with deep expertise in Nigeria-focused media, politics, and socio-economic research. Possessing a strong academic foundation, a growing record of peer-reviewed publications, and extensive international experience in university-level teaching and research. Proven ability to design and execute independent, high-quality projects using qualitative and mixed methods, including in-depth interviews, focus groups, thematic analysis, and systematic literature reviews. Experienced in sourcing, synthesising and fact-checking secondary, archival and media materials, and in preparing clear research outputs for academic and editorial audiences. Currently based in Lagos, Nigeria and available for remote collaboration and scheduled in-person interviews.}
%-------------------------------------------

%-----------ROLE ALIGNMENT-----------
\section{Researcher Role Alignment}
\resumeItemListStart
  \resumeItem{Conduct in-depth research on Nigeria's socio-economic and political history through rigorous use of secondary, archival and media sources}
  \resumeItem{Design interview frameworks, draft structured interview guides, and conduct physical and virtual interviews}
  \resumeItem{Compile, synthesise and clearly present research findings for editorial development and publication workflows}
  \resumeItem{Prepare, organise and copy-edit transcripts and research notes for clarity, usability and quality control}
  \resumeItem{Verify dates, facts, quotations and contextual references to uphold high standards of accuracy and credibility}
  \resumeItem{Collaborate effectively with distributed teams and deliver high-quality research outputs to deadline}
\resumeItemListEnd
%-------------------------------------------

%-----------PROFESSIONAL COMMITMENTS-----------
\section{Professional Commitments}
\small{Dedicated to fostering inclusive and equitable practices in research and teaching, aligning with values of care, continuous learning, and proactive engagement.}
%-------------------------------------------

%-----------RESEARCH INTERESTS-----------
\section{Research Interests}
    \resumeItemListStart
        \resumeItem{The role of media in democratic processes, particularly in relation to social investment programmes and poverty discourse in developing nations and the UK}
        \resumeItem{Independent journalism, its definitions, challenges, and impact within the UK and comparative contexts}
        \resumeItem{The interplay between traditional press, social media (Twittersphere), and public opinion}
        \resumeItem{Framing analysis, media representation of marginalized voices, and journalistic authenticity}
        \resumeItem{Contemporary research methodologies in communication and journalism, including systematic reviews and qualitative approaches}
        \resumeItem{Effective communication of research findings to academic, public, and potentially policy-relevant audiences}
    \resumeItemListEnd
%-------------------------------------------

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PhD in Journalism [no corrections]}{2025}
      {University of Kent}{UK}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis Title:} Poverty, Politics, and the Press: Uncovering the Complexities of Media Coverage on Nigeria's Social Investment Programmes}
        \resumeItem{Research employs quantitative, qualitative methods including in-depth interviews and thematic analysis using NVivo for In-depth Interview, SPSS for Content Analysis and CDA for twitter datasets}
        \resumeItem{\textbf{Supervisor(s):} Dr. Ben Cocking, Dr. Richard Pendry | \textbf{External Examiner:} Prof. Martin Scott}
      \resumeItemListEnd

    \resumeSubheading
      {Master of Science (M.Sc.), Communication Studies}{2019}
      {School of Communication, Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis Title:} ``Framing of President Muhammadu Buhari's UK medical Vacation by Nigerian Newspapers''}
      \resumeItemListEnd

    \resumeSubheading
      {Bachelor of Science (B.Sc.) (Hons), Mass Communication}{2014}
      {School of Communication, Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis Title:} ``Tabloidisation in the Nigerian Press: A Quantitative Investigation into Changes in Nigerian Newspapers, 2003 -- 2013''}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}

\subsection*{Doctoral Thesis (Completed 2025)}
    \resumeItemListStart
        \resumeItem{\textbf{Arowolo, O.S.} ``National Social Investment Programmes: the role of the press and Twittersphere in Nigeria.'' This research involved designing and executing a qualitative study, including conducting 10 in-depth interviews and 3 focus groups with journalists. Data analysis was conducted using NVivo software}
    \resumeItemListEnd

\subsection*{Current Research}
    \resumeItemListStart
    \resumeItem{Communicating Climate Change in Africa: Role Perception and Role Shifting Among Environmental Journalists in Nigeria}
    \resumeItem{Perceptions and Perspectives: Insights from East African Journalists on the Role of Artificial Intelligence in News Production}
        \resumeItem{Comparative study of independent journalism funding models in the UK and Nigeria}
        \resumeItem{\textbf{Arowolo, O.S.} ``Reclaiming authenticity in Nigerian press: a study of a National Social Investment Programme''}
        \resumeItem{\textbf{Arowolo, S.O.} ``The side-lined voice of the poor: slants and framing of poverty by the Nigerian print media''}
        \resumeItem{\textbf{Arowolo, S.O.} ``'Voices of the oppressed': an analysis of Nigeria Twittersphere conversations on Tradermoni poverty programme in Nigeria''}
        \resumeItem{\textbf{Arowolo, S.O.} ``What's up? News trading in the Nigerian press''}
        \resumeItem{\textbf{Arowolo, S.O.} and Oso, L. ``'Bottom-up news': do ordinary people matter in the news? -- a study of Tradermoni poverty programme in Nigeria''}
        \resumeItem{\textbf{Arowolo, S.O.} ``Echoing the frames: Eyes on Nigerian print media accounts of Lekki Toll Gate Massacre''}
    \resumeItemListEnd
%-------------------------------------------

%-----------TEACHING EXPERIENCE-----------
\section{Teaching Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lecturer (Media/Core Communication)}{November 2023 -- December 2024}
      {Health and Social Care, East Kent College, Ashford}{UK}
      \resumeItemListStart
        \resumeItem{Delivered engaging instruction in Health and Social Care to \textbf{76 students}, with focus on media communication relevant to the UK context}
        \resumeItem{Developed \textbf{8 tailored lesson plans} incorporating real-world media scenarios (audio-visual storytelling, communication ethics, media literacy)}
        \resumeItem{Assessed progress for 76 students, providing constructive feedback to enhance understanding of media and communication principles}
        \resumeItem{Collaborated with \textbf{3 colleagues} to align media aspects of the programme with industry standards, equipping students with skills applicable to health and media sectors}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer}{September 2022 -- 2023}
      {Centre for Journalism, University of Kent, Rochester}{UK}
      \resumeItemListStart
        \resumeItem{Delivered teaching for the \textbf{15-credit 'Studying Journalism' module (JOUR4050)}, covering key theories, debates, methodologies, and aspects of the UK journalism landscape, to approximately \textbf{23 undergraduate students per semester}}
        \resumeItem{Developed and delivered original teaching materials for \textbf{13 seminar groups}, enhancing student engagement with topics including journalism ethics, research methods, and contemporary UK media issues}
        \resumeItem{Set and marked assignments for approximately 23 students, providing timely and constructive feedback to support academic development}
        \resumeItem{Contributed to the planning and refinement of 1 teaching programme within the department}
        \resumeItem{Collaborated with \textbf{2 academic colleagues} on course development and curriculum updates for JOUR4050 -- 'Studying Journalism' module}
        \resumeItem{Mentored \textbf{4 undergraduate students} as a personal tutor, providing academic and pastoral support}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer (HPL)}{September 2021 -- 2022}
      {School of Social Policy, Sociology \& Social Research, University of Kent}{UK}
      \resumeItemListStart
        \resumeItem{Led seminar teaching for modules \textbf{SOCI3370} (Autumn, 12 seminars) and \textbf{SOCI5750} (Spring, 13 seminars) for approximately \textbf{142 students}}
        \resumeItem{Developed instructional materials and learning aids for seminar groups}
        \resumeItem{Evaluated student progress and provided feedback to approximately \textbf{56 students}}
        \resumeItem{Contributed to educational programme planning and curriculum revisions in collaboration with academic colleagues}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer}{June 2018 -- May 2021}
      {Department of Journalism, School of Communication, Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{Developed and delivered teaching materials for \textbf{over 950 undergraduate students} in Writing for Mass Media, Introduction to Photo Journalism, Photo-Journalism Management, Photo Editing and Newspaper and Magazine Production}
        \resumeItem{Supervised practical journalism work for \textbf{312 students}, advising on skills, methods, and techniques}
        \resumeItem{Conducted student assessments and contributed to research activities within the department}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Assistant}{June 2017 -- May 2018}
      {Department of Journalism, School of Communication, Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{Supported teaching and research activities, including delivering tutorial sessions for over \textbf{250 students}}
        \resumeItem{Assisted in developing teaching materials and overseeing practical work}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Assistant}{June 2015 -- April 2016}
      {Department of Languages, Linguistics, and Communication Studies, Osun State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{Assisted academic staff by conducting tutorial sessions for students in communication studies}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PUBLICATIONS-----------
\section{Publications}

\subsection{Projects and Dissertations (Theses)}
    \resumeItemListStart
        \resumeItem{\textbf{Arowolo, S.O.} (2019). Framing of President Muhammadu Buhari's UK medical Vacation by Nigerian Newspapers. M.Sc. Dissertation, Lagos State University}
        \resumeItem{\textbf{Arowolo, S.O.} (2015). Tabloidization in the Nigerian Press: A Quantitative Investigation into Changes in Nigerian Newspapers, 2003 -- 2013. B.Sc. Dissertation, Lagos State University}
    \resumeItemListEnd

\subsection{Articles in Peer-Reviewed Journals}
    \resumeItemListStart
        \resumeItem{Shodipe, O.A., \textbf{Arowolo, O.}, Oloyede, I.B., Alade, M., Fadeyi, I.O. and Oko-Epelle, L. (2024), Visual portrayal of Monkeypox outbreak on BBC: is Western media biased against Africa?, \textit{Global Knowledge, Memory and Communication}, Vol. ahead-of-print No. ahead-of-print. \href{https://doi.org/10.1108/GKMC-09-2023-0317}{https://doi.org/10.1108/GKMC-09-2023-0317}}
        \resumeItem{Oso Lai, Adeniran, R., \& \textbf{Arowolo, O.} (2024). Journalism Ethics: The Dilemma, Social and Contextual Constraints. \textit{Cogent Social Sciences}. \href{https://doi.org/10.1080/23311886.2024.2328388}{https://doi.org/10.1080/23311886.2024.2328388}}
        \resumeItem{\textbf{Arowolo, O.}, Yusuf, K., Yahya, J., Lambo, O. and Oduolowu, D. (2023). World Bank Concept of Good Governance, Contemporary Nigerian Democracy, and the Place of the Media. \textit{East African Journal of Interdisciplinary Studies}, 6(1), pp. 54-69. \href{https://doi.org/10.37284/eajis.6.1.1058}{https://doi.org/10.37284/eajis.6.1.1058}}
        \resumeItem{Suleiman, H., Adedeji, K., \& \textbf{Arowolo, S. O.} (2020). Online Newspaper Coverage of the 8th National Assembly in Nigeria. \textit{Media and Communication Review (MCR)}, Vol. 2, Issue 2, pp. 57--83}
        \resumeItem{Asomba, I.T. and \textbf{Arowolo, S.O.} (2018). Politics of Nigerian Newspaper Coverage of Ondo State 2012 Gubernatorial Election. \textit{Media and Communication Review (MCR)}, Vol. 3, Issue 1, pp. 85-109}
        \resumeItem{\textbf{Arowolo, S.O.} (2015). Uses and Gratification theory and Tobacco Advertising necessity: An Exposé. \textit{International Journal of Broadcasting and Information Technology}, 3(1). Lagos: Department of Broadcasting, School of Communication, Lagos State University}
    \resumeItemListEnd

\subsection{Chapters in Edited Books}
    \resumeItemListStart
        \resumeItem{\textbf{Arowolo, O.S.} \& Animashaun, O. W. (2020). Text Language: A Revolution in Modern Communication. In \textit{Book in Honour Professor Lai Oso at 60}. Research and Book Publication Committee, School of Communication, Lagos State University, Lagos Nigeria}
        \resumeItem{Oso, Lai, Adeniran, R. and \textbf{Arowolo, S. O.} (2019). The challenges and implications of health journalism practice in Nigeria newspapers. In A.M. Adeyanju, I. Jimoh \& H.M. Suleiman (Eds.). \textit{Mass Media in Nigeria: Research, theories, and practice: A book in honour of Prof. Suleiman Salau} (pp. 115-139). Jos: The National Institute, Kuru, Nigeria}
        \resumeItem{Oso, L. and \textbf{Arowolo, S. O.} (2019). Commercialisation and tabloidisation: Journalism as infotainment. In L. Oso, R. Olatunji, O. Omojola \& S. Oyero, \textit{Beyond fun: Media Entertainment, Politics and Development in Nigeria} (pp. 189-205). Lagos: Malthouse Press Limited}
    \resumeItemListEnd
%-------------------------------------------

%-----------CONFERENCE PAPERS-----------
\section{Conference Papers}
    \resumeItemListStart
    \resumeItem{\textbf{Arowolo, S. Olasunkanmi}. (2026). Electoral Weaponisation of Micro-Credit: Nigerian Newspaper Coverage of Tradermoni Vote-Buying Allegations During the 2018--2019 Election Cycle. Accepted for Individual Submission presentation at the 76th Annual Conference of the International Communication Association (ICA), 4--8 June 2026, Westin Cape Town \& CTICC, Cape Town, South Africa}
    \resumeItem{\textbf{Arowolo, S. Olasunkanmi}. (2026). Whose Voice Counts? Government Dominance and Press Release Reliance in Nigerian Newspaper Coverage of Social Investment Programmes. Accepted for Individual Submission presentation at the 76th Annual Conference of the International Communication Association (ICA), 4--8 June 2026, Westin Cape Town \& CTICC, Cape Town, South Africa}
        \resumeItem{Damilola Oduolowu and \textbf{Arowolo, S. Olasunkanmi}. (May 2025). Communicating Climate Change in Africa: Role perception and role shifting among environmental journalists in Nigeria. Paper to be presented at Public Communication of Science and Technology Network (PCST) 2025 on ``Using Science Communication to effect positive change: exploring transitions, traditions and tensions''}
        \resumeItem{\textbf{Arowolo, S. Olasunkanmi}. (2024, March). Harnessing the Fourth Estate: News media as catalyst for Effective Social Investment policies implementation. Paper presented at the AEJMC Midwinter Conference (Political Communication Division), Gaylord College of Journalism and Mass Communication, March 7-9, 2024 at the University of Oklahoma, in Norman, OK}
        \resumeItem{\textbf{Arowolo, S. Olasunkanmi} and Damilola Oduolowu (2024) Cross-Border Perspectives- A Comparative Thematic Analysis of Local Governance Discourse in US and UK Online Community News. Paper presented at the 2024 AEJMC Southeast Colloquium, 49th annual AEJMC Southeast Colloquium, March 1-2, 2024 at the University of Kentucky in Lexington, Kentucky}
        \resumeItem{Oso, Lai and \textbf{Arowolo, S. Olasunkanmi}. (2018, September). Hate Speech and Negotiating meaning. Paper presented at the 5th ACSPN Annual Conference on 'Hate Speech, Fake News and Political Stability in Africa', Asaba, Nigeria}
        \resumeItem{\textbf{Arowolo, S. Olasunkanmi} and Akano, M. M. (2018, September). New media, and attitude of students towards Online-Shopping: A case of Jumia.ng. Paper presented at the Afe-Babalola University, Ado-Ekiti (ABUAD)-Media, Communication, Information Technology (MCIT) 2018 International Conference, Ado-Ekiti, Ekiti State}
        \resumeItem{Biobaku, M.O., \textbf{Arowolo, S.O.}, Odesanya, L.A., \& Fatonji, S. (2018). Influence of 'The Lion of Bourdillon' Documentary on the Voting Intentions of Lagos Electorates in Nigeria's 2015 General Elections. Paper presented at the 2018 Press Freedom Day Conference}
        \resumeItem{Ogundoyin, S.O. and \textbf{Arowolo, S.O.} (2018). Media Advocacy Theory: A content analysis of media coverage of Nigerians' migration to Europe via Libya. Paper presented at the 2018 ACCE National Conference, National Open University of Nigeria, Abuja}
        \resumeItem{Oso, L., Jimoh, J., \& \textbf{Arowolo, O.S.} (2017, September). 3Ws: The social composition of news in selected Nigerian newspapers. Paper presented at the Association of Communication Scholars and Professionals of Nigeria (ACSPN) Conference, Bayero University, Kano (BUK)}
        \resumeItem{Suleiman, H.B., \textbf{Arowolo, O.S.} and Olona, K.A. (2016, September). Legislative Reporting in Nigeria: Online Newspaper 100 days Coverage of the 8th National Assembly Resolution. Paper presented at the Ebenezer Soola Conference on Communication change management and sustainable development in the 21st century, University of Ibadan, Ibadan, Nigeria}
    \resumeItemListEnd
%-------------------------------------------

%-----------SKILLS AND ABILITIES-----------
\section{Skills and Abilities}

\subsection{Research Methods \& Analysis:}
    \resumeItemListStart
        \resumeItem{\textbf{Qualitative Research:} Experienced in designing and conducting qualitative studies, including In-depth Interviews and Focus Groups. Proficient in qualitative data analysis techniques such as Thematic Analysis, Content Analysis, and Discourse Analysis}
        \resumeItem{\textbf{Quantitative Research:} Experienced in quantitative research design, surveys, basic statistical analysis, and Content Analysis}
        \resumeItem{\textbf{Literature Reviews:} Proficient in conducting comprehensive literature searches and developing Systematic Literature Reviews}
        \resumeItem{\textbf{Software:} NVivo, SPSS, Qualtrics, Microsoft Office Suite}
        \resumeItem{\textbf{UK Journalism Landscape:} Strong understanding developed through PhD research at a UK university, teaching UK journalism modules, and ongoing engagement with UK media}
    \resumeItemListEnd

\subsection{Communication \& Dissemination:}
    \resumeItemListStart
        \resumeItem{\textbf{Academic Writing:} Proven ability to draft and publish peer-reviewed journal articles, book chapters, and conference papers}
        \resumeItem{\textbf{Presentation Skills:} Experienced in delivering engaging academic presentations and lectures to diverse student groups}
        \resumeItem{\textbf{Public Communication:} Experience in journalism practice translating complex information for broader audiences}
    \resumeItemListEnd

\subsection{Project Management:}
    \resumeItemListStart
        \resumeItem{Research Project Management (design, execution, analysis, dissemination)}
        \resumeItem{Newspaper Management (previous experience)}
    \resumeItemListEnd

\subsection{Languages:}
    \resumeItemListStart
        \resumeItem{English (Fluent), Yoruba (Native)}
    \resumeItemListEnd
%-------------------------------------------

%-----------ADMINISTRATIVE EXPERIENCE-----------
\section{Administrative Experience}
    \resumeItemListStart
        \resumeItem{Contributed to planning of teaching programmes, Centre for Journalism, University of Kent (2022-Present)}
        \resumeItem{Collaborated on course development and curriculum changes, Centre for Journalism, University of Kent (2022-Present)}
    \resumeItemListEnd
%-------------------------------------------

%-----------AWARDS AND FUNDING-----------
\section{Awards and Funding}
    \resumeItemListStart
    \resumeItem{\textbf{Michael Haley Travel Grant} (\$700.00), awarded for the \textit{76th Annual ICA Conference: Communication and Inequalities in Context}, 4--8 June 2026, Cape Town, South Africa}
        \resumeItem{\textbf{Global Talent Endorsement}, British Academy (2025) -- Recognised as an exceptional promise in academia and research}
        \resumeItem{\textbf{Tertiary Education Trust Fund (TETFund)}, Federal Government of Nigeria University Doctoral Scholarship, University of Kent, 2021-2025}
        \resumeItem{\textbf{3-Minutes Thesis -- Runner up} (University of Kent) - 2024}
    \resumeItemListEnd
%-------------------------------------------

%-----------PROFESSIONAL ASSOCIATIONS-----------
\section{Professional Associations}
    \resumeItemListStart
        \resumeItem{Member, International Communication Association (ICA)}
        \resumeItem{Member, Public Communication of Science and Technology (PCST)}
        \resumeItem{Member, Association of Communication Scholars, and Professionals of Nigeria (ACSPN)}
        \resumeItem{Member, African Council for Communication Education (ACCE)}
    \resumeItemListEnd
%-------------------------------------------

%-----------EDITORIAL EXPERIENCE-----------
\section{Editorial Experience}
    \resumeItemListStart
        \resumeItem{\textbf{Blind Peer Reviewer}, Global Knowledge, Memory and Communication (Q2 Journal)}
        \resumeItem{\textbf{Blind Peer Reviewer}, Taylor and Francis}
    \resumeItemListEnd
%-------------------------------------------

%-----------LEADERSHIP ROLES-----------
\section{Leadership Roles}
    \resumeItemListStart
        \resumeItem{\textbf{Founder and CEO}, Afriscribe (\href{https://afriscribe.org}{afriscribe.org})}
        \resumeItem{\textbf{Director and Founder}, ResearchAfrica (\href{https://researchafrica.pub}{researchafrica.pub})}
    \resumeItemListEnd
%-------------------------------------------

%-----------REFERENCES-----------
\section{References}
  \resumeItemListStart
    \resumeItem{\textbf{Prof. Martin Scott}\\
    Professor in Media \textbar\ Development, School of Global Development, University of East Anglia\\
    University of East Anglia, Norwich Research Park, Norwich, NR4 7TJ\\
    \href{mailto:Martin.Scott@uea.ac.uk}{Martin.Scott@uea.ac.uk} | 1559}

    \resumeItem{\textbf{Dr Ben Cocking}\\
    Reader and Director of Research, Centre for Journalism\\
    Centre for Journalism, University of Kent\\
    \href{mailto:b.cocking@kent.ac.uk}{b.cocking@kent.ac.uk} | +44 (0)1634 888987}

    \resumeItem{\textbf{Prof. Jide Jimoh}\\
    Journalism, Lagos State University\\
    School of Communication, Lagos State University\\
    \href{mailto:jidejimoh@gmail.com}{jidejimoh@gmail.com} | +234 803 343 0764}
  \resumeItemListEnd
%-------------------------------------------

\newpage
\newgeometry{left=1in,right=1in,top=1in,bottom=1in}
\begingroup
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\fontsize{12pt}{15pt}\selectfont
\onehalfspacing

\begin{flushright}
Dr Olasunkanmi S. Arowolo \\
Lagos, Nigeria \\
+234 08062081819 \\
\href{mailto:oa@olaarowolo.com}{oa@olaarowolo.com} \\
20 February 2026
\end{flushright}

The Hiring Team \\
The Republic

\textbf{Dear Hiring Team,}

\textbf{Re: Application for Researcher (Two-Month Remote Project)}

I am writing to apply for the Researcher role at \textit{The Republic}. I am a PhD-trained journalism researcher with a strong record of Nigeria-focused research on politics, media, and socio-economic policy. Your call for rigorous historical research, careful interviewing, and source-driven analysis aligns directly with my training and practice.

My doctoral research at the University of Kent, \textit{Poverty, Politics, and the Press: Uncovering the Complexities of Media Coverage on Nigeria's Social Investment Programmes}, required exactly the type of work this role demands: identifying and synthesising secondary literature, analysing media archives, building evidence trails, and conducting and interpreting interview data. I designed interview guides, conducted in-depth interviews and focus groups, and produced clear findings for academic and policy-relevant audiences.

Beyond my PhD, my publications and conference work show sustained engagement with Nigerian politics, journalism, and public discourse. I have also developed strong editorial discipline through peer-review work and research writing, including checking claims, dates, quotations, and contextual framing for accuracy. I am comfortable preparing transcripts, refining research materials, and working to demanding deadlines.

I am currently based in Lagos, Nigeria for the coming months, available for remote collaboration with your editorial team and for scheduled in-person interviews where required. I would welcome the opportunity to contribute rigorous, reflective, and high-quality research to \textit{The Republic}'s reporting and analysis.

Thank you for your consideration. I would be glad to discuss how my background can support your project immediately.

\textbf{Yours faithfully,}

\vspace{2cm}

Dr Olasunkanmi S. Arowolo

\endgroup
\restoregeometry

\end{document}