\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{setspace}

\geometry{left=1in,right=1in,top=1in,bottom=1in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}
\onehalfspacing

\begin{document}

\begin{flushright}
Dr Olasunkanmi S. Arowolo \\
Lagos, Nigeria \\
+234 08062081819 \\
\href{mailto:oa@olaarowolo.com}{oa@olaarowolo.com} \\
20 February 2026
\end{flushright}

The Hiring Team \\
The Republic

\textbf{Dear Hiring Team,}

\textbf{Re: Application for Researcher (Two-Month Remote Project)}

I am writing to apply for the Researcher role at \textit{The Republic}. I am a PhD-trained journalism researcher with a strong record of Nigeria-focused research on politics, media, and socio-economic policy. Your call for rigorous historical research, careful interviewing, and source-driven analysis aligns directly with my training and practice.

My doctoral research at the University of Kent, \textit{Poverty, Politics, and the Press: Uncovering the Complexities of Media Coverage on Nigeria's Social Investment Programmes}, required exactly the type of work this role demands: identifying and synthesizing secondary literature, analysing media archives, building evidence trails, and conducting and interpreting interview data. I designed interview guides, conducted in-depth interviews and focus groups, and produced clear findings for academic and policy-relevant audiences.

Beyond my PhD, my publications and conference work show sustained engagement with Nigerian politics, journalism, and public discourse. I have also developed strong editorial discipline through peer-review work and research writing, including checking claims, dates, quotations, and contextual framing for accuracy. I am comfortable preparing transcripts, refining research materials, and working to demanding deadlines.

I am currently based in Lagos, Nigeria for the coming months, available for remote collaboration with your editorial team and for scheduled in-person interviews where required. I would welcome the opportunity to contribute rigorous, reflective, and high-quality research to \textit{The Republic}'s reporting and analysis.

Thank you for your consideration. I would be glad to discuss how my background can support your project immediately.

\textbf{Yours faithfully,}

\vspace{1cm}

Dr Olasunkanmi S. Arowolo

\end{document}
