\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CURRICULUM VITAE STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape CURRICULUM VITAE} \\
    \vspace{5pt}
    \textbf{\Large Dr Olasunkanmi S. Arowolo} \\ \vspace{1pt}
    \small Rochester, Kent, United Kingdom $|$ +44 (0)7487 397751 $|$ \href{mailto:oa@olaarowolo.com}{{oa@olaarowolo.com}} \\
    \vspace{3pt}
    \small \faLinkedin\ \href{https://www.linkedin.com/in/olaarowolo/}{linkedin.com/in/olaarowolo} $|$ 
    \faOrcid\ \href{https://orcid.org/0000-0002-5296-6478}{0000-0002-5296-6478} $|$ 
    \faGraduationCap\ \href{https://scholar.google.com/citations?user=3N_RQWoAAAAJ&hl=en}{Google Scholar} \\
    \vspace{2pt}
    \small \faResearchgate\ \href{https://www.researchgate.net/profile/Sunday-Arowolo}{ResearchGate} $|$ 
    \faTwitter\ \href{https://twitter.com/olaarowolo}{@olaarowolo}
\end{center}

% Set left alignment for all content after header
\raggedright

%-------------------------------------------

%-----------PROFESSIONAL PROFILE-----------
\section*{Professional Profile}
\small{Highly motivated and skilled Post-Doctoral candidate with a PhD in Journalism, endorsed by the British Academy as GlobalTalent in Media and Communication (2025). Possessing a strong academic foundation, a growing record of peer-reviewed publications, and extensive international experience in university-level teaching, including in the UK. Proven ability to design and execute independent, high-quality research projects, including proficiency in qualitative methodologies such as interviews and focus groups, and experience with systematic literature reviews. Actively engaged with the UK journalism landscape through research and teaching. Committed to contributing to impactful research, fostering an inclusive and equitable academic environment, and effectively communicating findings to diverse audiences.}
%-------------------------------------------

%-----------RESEARCH INTERESTS-----------
\section*{Research Interests}
    \resumeItemListStart
        \resumeItem{The role of media in democratic processes, particularly in relation to social investment programmes and poverty discourse in developing nations and the UK}
        \resumeItem{Independent journalism, its definitions, challenges, and impact within the UK and comparative contexts}
        \resumeItem{The interplay between traditional press, social media (Twittersphere), and public opinion}
        \resumeItem{Framing analysis, media representation of marginalized voices, and journalistic authenticity}
        \resumeItem{Contemporary research methodologies in communication and journalism, including systematic reviews and qualitative approaches}
        \resumeItem{Effective communication of research findings to academic, public, and potentially policy-relevant audiences}
    \resumeItemListEnd
%-------------------------------------------

%-----------ACADEMIC QUALIFICATIONS-----------
\section*{Academic Qualifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PhD in Journalism [no corrections]}{2025}
      {University of Kent}{United Kingdom}
      \resumeItemListStart
        \resumeItem{\textbf{Thesis Title:} Poverty, Politics, and the Press: Uncovering the Complexities of Media Coverage on Nigeria's Social Investment Programmes}
        \resumeItem{Research employs quantitative, qualitative methods including in-depth interviews and thematic analysis using NVivo, SPSS, and CDA}
        \resumeItem{\textbf{Supervisor(s):} Dr. Ben Cocking, Dr. Richard Pendry | \textbf{External Examiner:} Prof. Martin Scott}
      \resumeItemListEnd
    
    \resumeSubheading
      {Master of Science (M.Sc.), Communication Studies [4.01 CGPA]}{2019}
      {Lagos State University}{Nigeria}
    
    \resumeSubheading
      {Bachelor of Science (B.Sc.) (Hons), Mass Communication [4.1 CGPA]}{2014}
      {Lagos State University}{Nigeria}
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------RESEARCH EXPERIENCE-----------
\section*{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Assistant (British Academy-GRCF funded Project)}{2022 -- 2023}
      {University of Kent}{UK}
      \resumeItemListStart
        \resumeItem{PNEUMA-CITY: Frictional infrastructure, road ecologies and valorisation of end-of-life tyres (ELTs) towards more sustainable urban economies in West African mega-cities}
        \resumeItem{Part of the wider GCRF 'Urban Infrastructures of Well-Being' research programme}
        \resumeItem{Project website: \href{https://pneuma-city.org/}{https://pneuma-city.org/}}
      \resumeItemListEnd

    \resumeSubheading
      {Master's Thesis Research}{2019}
      {Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{``Framing of President Muhammadu Buhari's UK medical Vacation by Nigerian Newspapers''}
      \resumeItemListEnd

    \resumeSubheading
      {B.Sc. Research Project}{2014}
      {Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{``Tabloidisation in the Nigerian Press: A Quantitative Investigation into Changes in Nigerian Newspapers, 2003 -- 2013''}
      \resumeItemListEnd

    \resumeSubheading
      {Current Research Projects}{2024 -- Present}
      {Independent Research}{UK/Nigeria}
      \resumeItemListStart
        \resumeItem{\textbf{Mapping the Contemporary Nigerian Newsroom:} Defining Professional Identity in Contemporary Nigerian Journalism: A Nationwide Survey of Media Workers. \textit{Principal Investigator: Olasunkanmi Arowolo; Research Assistant: Matthew Ogunsuada}}
        \resumeItem{\textbf{Bridging the Gap Between Scientific Research and Public Engagement in Nigeria:} Rethinking Media Practices in the Digital Age. \textit{Principal Investigator: Olasunkanmi Arowolo}}
        \resumeItem{\textbf{Positioning Nigerian Newspapers on the Political Spectrum:} An Empirical Analysis of Editorial Slants and Issue Coverage. \textit{Principal Investigator: Olasunkanmi Arowolo}}
        \resumeItem{Comparative study of independent journalism funding models in the UK and Nigeria}
        \resumeItem{``The side-lined voice of the poor: slants and framing of poverty by the Nigerian print media''}
        \resumeItem{``'Voices of the oppressed': an analysis of Nigeria Twittersphere conversations on poverty programmes''}
        \resumeItem{``Echoing the frames: Nigerian print media accounts of Lekki Toll Gate Massacre''}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------RESEARCH SCHOLARSHIP AND AWARDS-----------
\section*{Research Scholarship and Awards}
    \resumeItemListStart
      \resumeItem{\textbf{Michael Haley Travel Grant} (\$700.00), awarded February 2026 for the \textit{76th Annual ICA Conference: Communication and Inequalities in Context}, 4--8 June 2026, Cape Town, South Africa}
        \resumeItem{\textbf{Global Talent Endorsement}, British Academy (2025) -- Recognised as an exceptional talent in academia and research}
        \resumeItem{\textbf{PhD in Journalism}, University of Kent (2025, no corrections)}
        \resumeItem{\textbf{TETFund Doctoral Scholarship} (£115,485.00)}
        \resumeItem{\textbf{Runner-Up}, University of Kent Three Minute Thesis (3MT, 2024)}
    \resumeItemListEnd
%-------------------------------------------

%-----------PROFESSIONAL MEMBERSHIP-----------
\section*{Professional Membership}
    \resumeItemListStart
        \resumeItem{Royal African Society (RAS), United Kingdom -- Member (2025)}
        \resumeItem{International Communication Association (ICA) -- Member (2022)}
        \resumeItem{Public Communication of Science and Technology (PCST) -- Member (2025)}
        \resumeItem{Association of Communication Scholars, and Professionals of Nigeria (ACSPN) -- Member (2014)}
        \resumeItem{African Council for Communication Education (ACCE) -- Member (2018)}
    \resumeItemListEnd
%-------------------------------------------

%-----------PROFESSIONAL & TECHNICAL QUALIFICATIONS-----------
\section*{Professional \& Technical Qualifications}
    \resumeItemListStart
        \resumeItem{ISC² Certified in Cybersecurity (2024)}
        \resumeItem{Qualys Certified Specialist (2024)}
        \resumeItem{Vulnerability Management Diploma}
    \resumeItemListEnd
%-------------------------------------------

%-----------RESEARCH FUNDING BID-----------
\section*{Research Funding Bid}
    \resumeItemListStart
        \resumeItem{\textbf{Arowolo, S.O.} (Principal Investigator). \textit{Media, Poverty, and Democracy: A Comparative Analysis of Social Investment Discourse in the UK and Nigeria.} Scheduled for submission to British Academy Small Research Grants (Spring 2026).}
        \resumeItem{\textbf{Arowolo, S.O.} (Principal Investigator). \textit{Democracy by Design? Comparative Governance of Algorithmic Journalism in the UK and Nigeria.} Targeting BA/Royal Society Interdisciplinary Scheme (Q1 2026).}
        \resumeItem{\textbf{Arowolo, S.O.} (Co-PI). \textit{Sustainable Journalism Ecosystems in Nigeria: Funding Models, Innovation and Policy for Media Resilience.} Proposal in development for Leverhulme Trust Research Project Grants}
    \resumeItemListEnd

%-------------------------------------------

%-----------EMPLOYMENT-----------
\section*{Employment}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lecturer (Media/Core Communication)}{November 2023 -- December 2024}
      {Health and Social Care, East Kent College, Ashford}{UK}
      \resumeItemListStart
        \resumeItem{Delivered engaging instruction in Health and Social Care to 76 students, with focus on media communication}
        \resumeItem{Developed eight tailored lesson plans incorporating real-world media scenarios}
        \resumeItem{Assessed progress for 76 students, providing constructive feedback}
        \resumeItem{Collaborated with three colleagues to align media aspects with industry standards}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer}{September 2022 -- 2023}
      {Centre for Journalism, University of Kent, Rochester}{UK}
      \resumeItemListStart
        \resumeItem{Delivered teaching for 15-credit 'Studying Journalism' module (JOUR4050) to 23 undergraduate students per semester}
        \resumeItem{Developed and delivered original teaching materials for 13 seminar groups}
        \resumeItem{Set and marked assignments for approximately 23 students}
        \resumeItem{Mentored four undergraduate students as personal tutor}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer (HPL)}{September 2021 -- 2022}
      {School of Social Policy, Sociology \& Social Research, University of Kent}{UK}
      \resumeItemListStart
        \resumeItem{Led seminar teaching for modules SOCI3370 and SOCI5750 for approximately 142 students}
        \resumeItem{Developed instructional materials and learning aids for seminar groups}
        \resumeItem{Evaluated student progress and provided feedback to approximately 56 students}
      \resumeItemListEnd

    \resumeSubheading
      {Assistant Lecturer}{June 2018 -- May 2021}
      {Department of Journalism, School of Communication, Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{Developed and delivered teaching materials for 950 undergraduate courses}
        \resumeItem{Supervised practical journalism work for 312 students}
        \resumeItem{Conducted student assessments and contributed to research activities}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Assistant}{June 2017 -- May 2018}
      {Department of Journalism, School of Communication, Lagos State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{Supported teaching and research activities for over 250 students}
        \resumeItem{Assisted in developing teaching materials and overseeing practical work}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Assistant}{June 2015 -- April 2016}
      {Department of Languages, Linguistics, and Communication Studies, Osun State University}{Nigeria}
      \resumeItemListStart
        \resumeItem{Assisted academic staff by conducting tutorial sessions for students in communication studies}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------ACADEMIC TRAININGS-----------
\section*{Academic Trainings (Selected)}
    \resumeItemListStart
        \resumeItem{Preparing \& Delivering Lectures, University of East Anglia}
        \resumeItem{Assessment, Feedback, \& Module Design, University of East Anglia}
        \resumeItem{Preparing Impactful Research Proposals \& Grant Applications, University of East Anglia}
        \resumeItem{Using the Media to Publicise Research, Graduate Research College, University of Kent}
        \resumeItem{Using NVivo for Qualitative Research, University of East Anglia}
        \resumeItem{Advanced Skills in NVivo, Graduate Research College, University of Kent}
    \resumeItemListEnd
%-------------------------------------------

%-----------PUBLICATIONS-----------
\section*{Publications}
\subsection*{Peer-Review Journals (Selected)}
    \resumeItemListStart
        \resumeItem{Shodipe, O.A., \textbf{Arowolo, O.}, Oloyede, I.B., Alade, M., Fadeyi, I.O. and Oko-Epelle, L. (2024), Visual portrayal of Monkeypox outbreak on BBC: is Western media biased against Africa?, \textit{Global Knowledge, Memory and Communication}. \href{https://doi.org/10.1108/GKMC-09-2023-0317}{https://doi.org/10.1108/GKMC-09-2023-0317}}
        \resumeItem{Oso Lai, Adeniran, R., \& \textbf{Arowolo, O.} (2024). Journalism Ethics: The Dilemma, Social and Contextual Constraints. \textit{Cogent Social Sciences}. \href{https://doi.org/10.1080/23311886.2024.2328388}{https://doi.org/10.1080/23311886.2024.2328388}}
        \resumeItem{\textbf{Arowolo, O.}, Yusuf, K., Yahya, J., Lambo, O. and Oduolowu, D. (2023). World Bank Concept of Good Governance, Contemporary Nigerian Democracy, and the Place of the Media. \textit{East African Journal of Interdisciplinary Studies}, 6(1), pp. 54-69. \href{https://doi.org/10.37284/eajis.6.1.1058}{https://doi.org/10.37284/eajis.6.1.1058}}
        \resumeItem{Suleiman, H., Adedeji, K., \& \textbf{Arowolo, S. O.} (2020). Online Newspaper Coverage of the 8th National Assembly in Nigeria. Media and Communication Review (MCR), Vol. 2, Issue 2, pp. 57–83}
        \resumeItem{Asomba, I.T. and \textbf{Arowolo, S.O.} (2018). Politics of Nigerian Newspaper Coverage of Ondo State 2012 Gubernatorial Election. Media and Communication Review (MCR), Vol. 3, Issue 1, pp. 85-109}
        \resumeItem{\textbf{Arowolo, S.O.} (2015). Uses and Gratification Theory and Tobacco Advertising Necessity: An Exposé. International Journal of Broadcasting and Information Technology, 3(1)}
    \resumeItemListEnd

\subsection*{Book Chapters}
    \resumeItemListStart
        \resumeItem{Oso, L., Jimoh, J. and \textbf{Arowolo, O.} (2022) ``3Ws: The Social Composition of News in Selected Nigerian Newspapers,'' Journal of Media, Theatre and Communication Studies (JOMETCOS), 1(2), pp. 1–17}
        \resumeItem{\textbf{Arowolo, O.S.} \& Animashaun, O. W. (2020). Text Language: A Revolution in Modern Communication. In Book in Honour of Professor Lai Oso at 60}
        \resumeItem{Oso, Lai, Adeniran, R. and \textbf{Arowolo, S. O.} (2019). The challenges and implications of health journalism practice in Nigerian newspapers. In A.M. Adeyanju, I. Jimoh \& H.M. Suleiman (Eds.). Mass Media in Nigeria: Research, theories, and practice}
        \resumeItem{Oso, L. and \textbf{Arowolo, S. O.} (2019). Commercialisation and tabloidisation: Journalism as infotainment. In L. Oso, R. Olatunji, O. Omojola \& S. Oyero, Beyond fun: Media Entertainment, Politics and Development in Nigeria}
    \resumeItemListEnd

\subsection*{Book/Monograph (in progress)}
    \resumeItemListStart
        \resumeItem{The Politics of Welfare Communication: Lessons from Media Coverage in the Global South and North. The book proposal is being prepared for Oxford University Press (OUP) and Cambridge University Press for consideration}
    \resumeItemListEnd

\subsection*{Accepted works}
    \resumeItemListStart
        \resumeItem{Oduolowu, D. and \textbf{Arowolo, O.} Perceptions and Perspectives: Insights from East African Journalists on the Role of Artificial Intelligence in News Production. Book Title: AI Revolution in Media and Communication – Shaping Teaching \& Practice in Africa | Publisher: Routledge}
    \resumeItemListEnd
%-------------------------------------------

%-----------SKILLS AND ABILITIES-----------
\section{Skills and Abilities}
\subsection*{Research Methods \& Analysis:}
    \resumeItemListStart
        \resumeItem{\textbf{Qualitative Research:} Experienced in designing and conducting qualitative studies, including In-depth Interviews and Focus Groups. Proficient in qualitative data analysis techniques such as Thematic Analysis, Content Analysis, and Discourse Analysis}
        \resumeItem{\textbf{Quantitative Research:} Experienced in quantitative research design, surveys, basic statistical analysis, and Content Analysis}
        \resumeItem{\textbf{Literature Reviews:} Proficient in conducting comprehensive literature searches and developing Systematic Literature Reviews}
        \resumeItem{\textbf{Software:} NVivo, SPSS, Qualtrics, Microsoft Office Suite}
        \resumeItem{\textbf{UK Journalism Landscape:} Strong understanding developed through PhD research at a UK university, teaching UK journalism modules, and ongoing engagement with UK media}
    \resumeItemListEnd

\subsection*{Communication \& Dissemination:}
    \resumeItemListStart
        \resumeItem{\textbf{Academic Writing:} Proven ability to draft and publish peer-reviewed journal articles, book chapters, and conference papers}
        \resumeItem{\textbf{Presentation Skills:} Experienced in delivering engaging academic presentations and lectures to diverse student groups}
        \resumeItem{\textbf{Public Communication:} Experience in journalism practice translating complex information for broader audiences}
        \resumeItem{\textbf{Languages:} English (Fluent), Yoruba (Native)}
    \resumeItemListEnd
%-------------------------------------------

%-----------CONFERENCES-----------
\section{Conferences}
    \resumeItemListStart
    \resumeItem{\textbf{Arowolo, S. Olasunkanmi}. (2026). Electoral Weaponisation of Micro-Credit: Nigerian Newspaper Coverage of Tradermoni Vote-Buying Allegations During the 2018--2019 Election Cycle. Accepted for Individual Submission presentation at the 76th Annual Conference of the International Communication Association (ICA), 4--8 June 2026, Westin Cape Town \& CTICC, Cape Town, South Africa}
    \resumeItem{\textbf{Arowolo, S. Olasunkanmi}. (2026). Whose Voice Counts? Government Dominance and Press Release Reliance in Nigerian Newspaper Coverage of Social Investment Programmes. Accepted for Individual Submission presentation at the 76th Annual Conference of the International Communication Association (ICA), 4--8 June 2026, Westin Cape Town \& CTICC, Cape Town, South Africa}
        \resumeItem{Damilola Oduolowu and \textbf{Arowolo, S. Olasunkanmi}. (May 2025). Communicating Climate Change in Africa: Role perception and role shifting among environmental journalists in Nigeria. Paper to be presented at Public Communication of Science and Technology Network (PCST) 2025}
        \resumeItem{\textbf{Arowolo, S. Olasunkanmi}. (2024, March). Harnessing the Fourth Estate: News media as catalyst for Effective Social Investment policies implementation. Paper presented at the AEJMC Midwinter Conference}
        \resumeItem{\textbf{Arowolo, S. Olasunkanmi} and Damilola Oduolowu (2024). Cross-Border Perspectives- A Comparative Thematic Analysis of Local Governance Discourse in US and UK Online Community News. Paper presented at the 2024 AEJMC Southeast Colloquium}
        \resumeItem{Oso, Lai and \textbf{Arowolo, S. Olasunkanmi}. (2018, September). Hate Speech and Negotiating Meaning. Paper presented at the 5th ACSPN Annual Conference}
        \resumeItem{\textbf{Arowolo, S. Olasunkanmi} and Akano, M. M. (2018, September). New media and the attitude of students towards Online Shopping: A case of Jumia.ng. Paper presented at the ABUAD-MCIT 2018 International Conference}
    \resumeItemListEnd
%-------------------------------------------

%-----------PUBLIC ENGAGEMENT-----------
\section{Selected: Public engagement, news mentions and articles in the news media}
    \resumeItemListStart
        \resumeItem{August 2025 – Nigeria must rethink its approach to poverty alleviation — Arowolo | Vanguard News}
        \resumeItem{August 2025 – Accolades as Nigerian Scholar Olasunkanmi Arowolo earns rare PhD distinction at UK Varsity |The Sun}
        \resumeItem{August 2025 – Study flags gaps in media coverage of Nigeria's poverty alleviation programmes. | Premium Times}
        \resumeItem{May 2025 – Zero conversations, zero accountability: The NSIP scandal |The Sun (Nigeria)}
    \resumeItemListEnd
%-------------------------------------------

%-----------ADMINISTRATIVE EXPERIENCE-----------
\section{Administrative Experience}
    \resumeItemListStart
        \resumeItem{Contributed to planning of teaching programmes, Centre for Journalism, University of Kent (2022-Present)}
        \resumeItem{Collaborated on course development and curriculum changes, Centre for Journalism, University of Kent (2022-Present)}
    \resumeItemListEnd
%-------------------------------------------

%-----------EDITORIAL EXPERIENCE-----------
\section{Editorial Experience}
    \resumeItemListStart
        \resumeItem{\textbf{Blind Peer Reviewer}, Global Knowledge, Memory and Communication (Q2 Journal)}
        \resumeItem{\textbf{Blind Peer Reviewer}, Taylor and Francis}
    \resumeItemListEnd
%-------------------------------------------

%-----------LEADERSHIP ROLES-----------
\section{Leadership Roles}
    \resumeItemListStart
        \resumeItem{\textbf{Founder and CEO}, Afriscribe (\href{https://afriscribe.org}{afriscribe.org})}
        \resumeItem{\textbf{Director and Founder}, ResearchAfrica (\href{https://researchafrica.pub}{researchafrica.pub})}
    \resumeItemListEnd
%-------------------------------------------

%-----------REFERENCES-----------
\section{References}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Professor Martin Scott}{University of East Anglia, UK}
      {Professor in Media \& Development, School of Global Development}{\href{mailto:martin.scott@uea.ac.uk}{martin.scott@uea.ac.uk}}

    \resumeSubheading
      {Dr Ben Cocking}{University of Kent, UK}
      {Reader \& Director of Research, Centre for Journalism}{\href{mailto:b.cocking@kent.ac.uk}{b.cocking@kent.ac.uk}}

    \resumeSubheading
      {Professor Adams Burgess}{University of Kent, UK}
      {Professor, School of Social Policy and Social Research}{\href{mailto:a.burgess@kent.ac.uk}{a.burgess@kent.ac.uk}}

    \resumeSubheading
      {Professor Winston Mano}{University of Westminster, UK}
      {Professor of Journalism, Communication and Media Research Institute (CAMRI)}{\href{mailto:W.Mano@westminster.ac.uk}{W.Mano@westminster.ac.uk}}

    \resumeSubheading
      {Professor Ola Ogunyemi}{University of Lincoln, UK}
      {Professor of Journalism}{\href{mailto:oogunyemi@lincoln.ac.uk}{oogunyemi@lincoln.ac.uk}}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}